---
title: "final_project"
output: html_document
date: "2023-11-22"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r }
library(dplyr)
np = read.table("np.csv", header=T, na.strings=".") %>%
  arrange(SubscriptionId, t) %>%
  group_by(SubscriptionId) %>%
  mutate(nextchurn = lead(churn),
  nextprice=lead(currprice),
  t = t)

summary(np)

```

## 2


nextchurn \~ t+trial+nextprice+regularity+intensity

```{r}
fit1=glm(nextchurn ~ t+trial+nextprice+regularity+intensity, np, family = "binomial")
summary(fit1)
vif(fit1)

```

nextchurn \~ t+trial+nextprice+regularity

```{r}
fit2=glm(nextchurn ~ t+trial+nextprice+regularity, np, family = "binomial")
summary(fit2)
```

nextchurn \~ t+trial+nextprice+intensity

```{r}
fit3=glm(nextchurn ~ t+trial+nextprice+intensity, np, family = "binomial")
summary(fit3)

```

```{r}
cor(np[, c("nextchurn","t","trial","nextprice","regularity","intensity")])
```

nextchurn \~ t+trial+nextprice+regularity+intensity -intensity not
significant

nextchurn \~ t+trial+nextprice+regularity -all predictors are
significant

nextchurn \~ t+trial+nextprice+intensity -all predictors are significant

intensity and regularity are correlated.

## 2a


coefficient for trial is positive. Meaning that a customer is more
likely to churn the next month when the customer pays trial rate vs when
the customer doesn't pay trial rate.

## 2b


The affect of regularity is larger than the affect of intensity due to
higher (in absolute value) coefficient.

## 3

Fit the following model to study content:
nextchurn\~t+trial+nextprice+sports1+news1+crime1+life1+obits1+business1
+opinion1 

```{r}
fit4=glm(nextchurn~t+trial+nextprice+sports1+news1+crime1+life1+obits1+business1
+opinion1, np, family = "binomial")
summary(fit4)
```

sports1 and news1 are contents that are statistically significant.

```{r}
# add in regularity
fit4_regularity=glm(nextchurn~t+trial+nextprice+sports1+news1+crime1+life1+obits1+business1
+opinion1+regularity, np, family = "binomial")
summary(fit4_regularity)

cor(np[, c("nextchurn","t","trial","nextprice", "intensity", "regularity","sports1","news1","crime1","life1","obits1","business1","opinion1","desktop", "tablet", "mobile" )])
```

No content predictors are statistically significant once we include
regularity. sports1 and news1 are highly correlated with
regularity(cor=0.5567141, 0.5516016 ).

Sports and news content is often time-sensitive, and users who read
regularly may be more inclined to stay informed and up-to-date with the
latest developments. This desire for timely information can drive higher
page views in these sections.

## 4

Model to study the effect of device on churn?

```{r}
fit5 <- glm(nextchurn~t+trial+nextprice+mobile+tablet+desktop, data = np, family = "binomial")
summary(fit5)
```

Only desktop is statistically significant. Customers who use a desktop
could indicate that they are more serious about news reading vs
customers who use a tablet/mobile device.

## 5

Use Lasso with cross validation rather than statistical significance,

```{r}
fit6=glm(nextchurn~t+trial+nextprice+sports1+news1+crime1+life1+obits1+business1
+opinion1+mobile+tablet+desktop, np, family = "binomial")
summary(fit6)
```

```{r}
library(glmnet)
set.seed(12345)
#drop na
no_na_np=na.omit(np)

x=model.matrix(nextchurn~t+trial+nextprice+sports1+news1+crime1+life1+obits1+business1
  +opinion1+mobile+tablet+desktop-1, no_na_np)
lam = exp(seq(-10, 7, length=100))
fit.l1 = cv.glmnet(x, no_na_np$nextchurn, alpha=1, lambda=lam, nfolds=5)

l=fit.l1$lambda.min
predict(fit.l1$glmnet.fit, s=l, type="coef")
```

Looking at pvalue: t, nextprice, trial, and desktop are significant.

Using lasso: t, nextprice, trial, sports1, news1, desktop, and tablet
are significant.

Overall recommendation: To improve churn rate, we recommend -special
offers for desktop users (games like the NYT wordle). -Release separate
sports issues. -Send out weekly newsletter focusing on news
(international, domestic). -Develop retention programs specifically
focused on users who engage with the sports and news sections. This
could include loyalty programs, rewards, or exclusive access to premium
content. -Segment your user base based on their interactions with the
sports and news sections. Tailor marketing and engagement strategies for
each segment to address their specific needs and preferences.

```{r}
cor(np[, c("nextchurn","t","trial","nextprice","regularity","intensity","sports1", "news1", "crime1", "life1","obits1","business1", "opinion1", "mobile", "tablet", "desktop")])
```
